Appendix A - Alternative DSDM formulations

### 2019-10-16 manuscript/appendix_a.Rmd
add toc to appendix A; fix typos

---
title: "Appendix A - Alternative DSDM formulations"
author:
  - Nick Golding
  - School of BioSciences, University of Melbourne, Parkville VIC, Australia
bibliography: dsdm.bib
csl: mee.csl
output:
  pdf_document:
  word_document:
    fig_caption: true
    highlight: null
---

@@

@@

top <- cbind(F * S_J, F * S_A)
bottom <- cbind(S_J, S_A)
A <- abind(top_row, bottom_row, along = 3)
```

@@

Code:
```{r negbin_obs}
p <- r / (r + Lambda)
distribution(y) <- negative_binomial(r, p)
```
Given a positive scalar `r`, and where y is a vector of counts.

>>>>

---
title: "Appendix A - Alternative DSDM formulations"
author:
  - Nick Golding
  - School of BioSciences, University of Melbourne, Parkville VIC, Australia
bibliography: dsdm.bib
csl: mee.csl
output:
  pdf_document:
    toc: true
    toc_depth: 2
  word_document:
    fig_caption: true
    highlight: null
---

@@

# Introduction

@@

top <- cbind(F * S_J, F * S_A)
bottom <- cbind(S_J, S_A)
A <- abind(top, bottom, along = 3)
```

@@

Code:
```{r negbin_obs}
p <- r / (r + Lambda)
distribution(y) <- negative_binomial(r, p)
```
Given a positive scalar `r`, and where y is a vector of counts. `r` and `p` correspond to the `size` and `prob` arguments of `stats::dnbinom` in R.
